### 2024-01-01 chapters/paper_retrospective.tex
Fix commas after equations

\textit{This chapter is a piece of original research published as part of the project:} \newline
\begin{center}
    \begin{enumerate}[leftmargin=8mm,rightmargin=8mm,topsep=0mm,label={[\Alph*]}]
        \setcounter{enumi}{5}
        \item \fullcite{wenstrup_retrospective_2023} \shared \hspace{0.1em} \parencite{wenstrup_retrospective_2023}
    \end{enumerate}
\end{center}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.98\textwidth]{paper_retrospective/figure2.pdf}
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \label{fig_retrospective:figure2-prediction-confusion-matrices}
\end{figure}

@@

We report the F1-score, sensitivity, PPV, FOR (equal to 1- negative predictive value), and FPR (equal to 1 - specificity). Due to the imbalanced nature of the dataset, the negative predictive value and specificity were greater than 99\% for all cases. We reported FOR and FPR instead because such large numerical values exhibit low relative variance, thereby obfuscating comparisons. Finally, we report the prediction confusion matrices, ROC curve, and PPV-sensitivity curve, commonly known as the precision-recall curve. All results are reported with up to three significant digits.

>>>>

\textit{This chapter is a piece of original research by the candidate, previously published elsewhere and reprinted here with permission:} \newline
\begin{center}
    \begin{enumerate}[leftmargin=8mm,rightmargin=8mm,topsep=0mm,label={[\Alph*]}]
        \setcounter{enumi}{5}
        \item \fullcite{wenstrup_retrospective_2023} \shared \hspace{0.1em} \parencite{wenstrup_retrospective_2023}
    \end{enumerate}
\end{center}

@@

\begin{table}[t]
    \centering
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \includegraphics[width=0.98\textwidth]{paper_retrospective/figure2.pdf}
    \label{fig_retrospective:figure2-prediction-confusion-matrices}
\end{table}

@@

We report the F1-score, sensitivity, PPV, FOR (equal to 1- negative predictive value), and FPR (equal to 1 - specificity). Due to the unbalanced nature of the dataset, the negative predictive value and specificity were greater than 99\% for all cases. We reported FOR and FPR instead because such large numerical values exhibit low relative variance, thereby obfuscating comparisons. Finally, we report the prediction confusion matrices, ROC curve, and PPV-sensitivity curve, commonly known as the precision-recall curve. All results are reported with up to three significant digits.
